### 2020-01-31 wuhan.tex
An apology of sorts ☺
let me pull

Here, we only focused on estimates of \Ro that were published within a very short frame of time.
Although our analysis reflects a snapshot of a fast moving epidemic, our lessons will hold: uncertainties in generation-interval distribution is important.
As the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will eventually decrease, 
and the effect of uncertainty in the mean generation time will become more important.

>>>>

Here, we only focused on estimates of \Ro that were published within a very short frame of time.
Although our analysis reflects a snapshot of a fast moving epidemic, our lessons will hold: understanding uncertainties in generation-interval distribution is important.
As the epidemic progresses and more data becomes available, inference on epidemic trajectories will become more precise.
Uncertainty in the exponential growth rate will inevitably decrease, 
and the effect of uncertainty in the mean generation time will become more important.
A recent epidemiological analysis of the patient-level data revealed large uncertainty in serial intervals, which is defined as the time between symptom onsets of an infector and an infectee, (mean: 7.5 days; 95\% CI: .3--19) \citep{nejmncov};
